|

### 2022-11-07 manuscript.Rmd
WIP: update intro

>>>>

Data science consits of iterative process importing, tidying, transforming, visualizing, and modeling data [@wickham2016r]. While each stage has unique challenges, data visualization may pose fundamental barriers against people with permanent, situational, and temporary disabiliteis (e.g., visual, cognitive, and motor impairments to name a few) in accessing information [@marriottInclusiveDataVisualization2021; @leeReachingBroaderAudiences2020]. For example, people with cognitive and learning disabilities often have difficulties understanding the abstractions and symbolic conventions used in visualizations, and people lacking fine motor coordination or having tremors may be unable to operate interactive visualizations not to mention people who are blind and have low vision facing extra challenges in visualization access [@marriottInclusiveDataVisualization2021]. @marriottInclusiveDataVisualization2021, in their call to action paper, highlights the serious impact of inaccessible visualizations: "this is an equity issue with severe consequences, because a lack of access to visualizations and underlying data impacts health, educational and work opportunities, and lifestyle." <!-- Need to find a specific page number for this quote. -->

Despite these
